User-level Grid Monitoring with Inca 2

### 2007-02-22 papers/hpdc-gmw-2007/paper.tex
word grammar pass
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6539 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{times}
\usepackage{url}

@@

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains which
requires a significant amount of coordination.  This is typically performed by
a group of Grid operators who take into account local site policies 
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured for the set of heterogeneous
resources.  Each site's system administrators, who are oftentimes not Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise inconsistencies between the resources arise that can either
inconvenience the user or prevent them from using particular resources
together.  Second, as a large distributed system, failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to detect such problems, 
monitoring of the resources is required.

@@

1.  Periodic tests executed by the monitoring system should be automated and
run from a standard user account.  A user GSI credential should be issued and
used by the monitoring system to test services that require authentication.  
%myproxy stuff
2.  Tests should be executed locally on all Grid resources when appropriate so
that all Grid access points available to users are tested.  
3.  The configuration of tests should be managed centrally in order to ensure
consistent testing of the resources, rather than by system administrators who
may not use the same information that is available to users.
4.  The testing system should easily adapt to new resources and testing
requirements.  In our experience, testing has an iterative refinement process
because Grids are dynamic and the software environment changes over time as
packages are upgraded.  Furthermore, it is often difficult to write and deploy
a test perfectly the first time because of portability issues and incomplete
user documentation.   
5.  System administrators should not need to know the details of the
monitoring system in order to troubleshoot problems.  When a problem is
detected the monitoring system should provide system administrators with
sufficient information to locate the problem easily and test repairs.
6.  A history of test results (especially any error messages) should be
retained in order to understand the behavior of their Grid over time. This
history should be available through a flexible querying interface.
7.  A running monitoring system should have a limited impact on the resources
it measures and should be secure.

%------------------------------------------------------------------------- 
\Section{Architecture}

@@

\begin{enumerate}
\item The Inca administrator creates a deployment configuration file using
incat and submits it to the agent.

@@

\noindent The following subsections describe the Inca components in more
detail in the order of the steps above.

@@

To configure reporter execution, an Inca administrator launches a GUI tool,
called incat.  Incat allows the administrator to choose which resources to
monitor and which reporters to deploy to those resources.  For each
reporter, the administrator can specify the resources to run on,
command-line arguments, the runtime environment, the frequency of execution,
and resource limits. The Inca administrator may also group related reporters
into suites that can be shared across different Inca deployments.  This can
be useful to determine interoperability among Grids or to determine whether
an application's requirements are being fulfilled on a Grid.

\subsubsection{Reporters}

Each Inca reporter is an executable program that tests or measures some
aspect of a system or installed software.   Reporter executables are
designed to be easy to produce and can be run outside of the Inca system
(e.g., by a system administrator).  A reporter could be a simple Globus
gatekeeper ping test (see Figure 2) or a more complex Grid application
benchmark.  Reporters must support certain command line options and produce
XML according to the Inca reporter schema.  The reporter schema requires a
header describing the context of the reporter execution (e.g., reporter
name, arguments, working directory, timestamp) and a body containing the
results expressed as any XML sequence. This flexible body schema enables
reporters to express a wide variety of information.  Today, we have three
standard body schemas to express software version information, software
functionality or service tests results, and usage information.  We provide
Perl APIs to handle much of the effort of writing reporters.  Most current
reporters use these APIs and consist of fewer than 30 lines of code.  
% capture context of execution

\subsubsection{Reporter Repositories}

The Inca agent retrieves reporters from collections called reporter
repositories, that consist of reporters, required packages and libraries,
and a catalog file. Repository contents are accessible using a URL and can
be shared across multiple Inca deployments. The Inca team publishes a
reporter repository that contains reporters developed for TeraGrid.

>>>>

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{times}
\usepackage{url}

@@

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid operators who take into account local site policies 
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured for the set of heterogeneous
resources.  Each site's system administrators, who are oftentimes not Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise inconsistencies between the resources arise that can either
inconvenience the user or prevent them from using particular resources
together.  Second, as a large distributed system, failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to detect such problems, 
monitoring of the resources is required.

@@

\begin{enumerate}
\item A reporter 
\item logging in reporters
\item Given the challenges of writing portable tests and benchmarks, Inca 2 
includes a set of Perl APIs that provide convenience functions to simplify
this process.

\item Periodic tests executed by the monitoring system should be automated and
run from a standard user account.  A user GSI credential should be issued and
used by the monitoring system to test services that require authentication.  
%myproxy stuff
\item Tests should be executed locally on all Grid resources when appropriate so
that all Grid access points available to users are tested.  
\item The configuration of tests should be managed centrally in order to ensure
consistent testing of the resources, rather than by system administrators who
may not use the same information that is available to users.
\item The testing system should easily adapt to new resources and testing
requirements.  In our experience, testing has an iterative refinement process
because Grids are dynamic and the software environment changes over time as
packages are upgraded.  Furthermore, it is often difficult to write and deploy
a test perfectly the first time because of portability issues and incomplete
user documentation.   
\item System administrators should not need to know the details of the
monitoring system in order to troubleshoot problems.  When a problem is
detected the monitoring system should provide system administrators with
sufficient information to locate the problem easily and test repairs.
\item A history of test results (especially any error messages) should be
retained in order to understand the behavior of their Grid over time. This
history should be available through a flexible querying interface.
\item A running monitoring system should have a limited impact on the resources
it measures and should be secure.
\end{enumerate}

%------------------------------------------------------------------------- 
\Section{Inca 2 Architecture}

@@

\begin{enumerate}

\item Using the guidelines described in the introduction, the Inca
administrator either writes reporters to monitor their Grid or uses existing
reporters in a published repository.

\item The Inca administrator creates a deployment configuration file that
describes the user-level monitoring for their Grid using incat and submits it
to the agent.

@@

\noindent The following subsections describe the Inca components in more
detail using the order of the steps above.

\SubSection{Reporters}

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) its sample output.}
\end{figure}

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written following the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML report according to
the Inca reporter schema.  The goal of the reporter schema is to accommodate
multiple types of data and to capture information about the reporter
execution to diagnose any detected failures.  The reporter schema consists of
the following elements:

\begin{itemize}
\item a set of header tags describing the context of the reporter
execution:  GMT timestamp, hostname, reporter name, reporter version, working
directory, reporter path, and arguments;
\item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
\item a body containing the results expressed as any XML sequence; and
\item an exit status tag
indicating whether the reporter was able to complete its test or measurement
and an optional error message.  
\end{itemize} 
\noindent Because the body of the report can be any XML sequence, it enables
reporters to express a wide variety of information.  Today, we have four
standard body schemas to express software version information, software
functionality or service tests results, usage information, and performance
results.

We provide an extensible set of Perl APIs to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
1-9,43-46).  It also includes some informational and debug logging functions
again similar to log4j; the log output has been very useful to system
administrators who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) and logs to the 'system'
level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema -- reporting software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
18, 20) depending on the output of system command.  And finally, the
Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
dependency to the reporter telling the Inca system to download a
short-term proxy before running this reporter (this is discussed further in
Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
fewer than 30 lines of code.

\SubSection{Reporter Repositories}

The Inca agent retrieves reporters from collections called reporter
repositories that consist of reporters, required packages and libraries,
and a catalog file. Repository contents are accessible using a URL and can
be shared across multiple Inca deployments. The Inca team publishes a
reporter repository that contains reporters developed for TeraGrid.

@@

The Inca administrative GUI tool (incat) is the main interface by which an
Inca administrator interacts with the Inca system.  Incat allows the Inca
administrator to view the choose which resources to monitor and which tests or 
benchmarks to deploy to those resources.  The following subsections
describe the Inca components that are configurable via incat.  
To configure reporter execution, an Inca administrator launches a GUI tool,
called incat.  Incat allows the administrator to choose which resources to
monitor and which reporters to deploy to those resources.  For each
reporter, the administrator can specify the resources to run on,
command-line arguments, the runtime environment, the frequency of execution,
and resource limits. The Inca administrator may also group related reporters
into suites that can be shared across different Inca deployments.  This can
be useful to determine interoperability among Grids or to determine whether
an application's requirements are being fulfilled on a Grid.
